Overview

### 2020-07-21 README.Rmd
More cleanup, ref #16
Add a Makefile to generate the documentation. ref #16
Update doc, add BTM Vignette
Inclde path for community contribution ref #31

@@

Please refer to the [overview of this package](vignettes/overview.md).

>>>>

<img src="man/figures/oolong_demo.gif" align="center" height="400" />

@@

Please refer to the [overview](overview_gh.md) for an introduction to this package. If you use BTM, please refer to the [BTM Vignette](btm_gh.md).

## Contributing

Contributions in the form of feedback, comments, code, and bug report are welcome.

* Fork the source code, modify, and issue a [pull request](https://docs.github.com/en/github/collaborating-with-issues-and-pull-requests/creating-a-pull-request-from-a-fork).
* Issues, bug reports: [File a Github issue](https://github.com/chainsawriot/oolong).
* Github is not your thing? Contact Chung-hong Chan by e-mail, post, or other methods listed on this [page](https://www.mzes.uni-mannheim.de/d7/en/profiles/chung-hong-chan).

## Code of Conduct

Please note that the oolong project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.

---
